### 2019-10-22 README.Rmd
pkgdown: use mlr3pkgdowntemplate
fix readme figs

Spatio-temporal extensions for mlr3

<!-- badges: start -->
[![Travis build status](https://travis-ci.org/mlr-org/mlr3spatiotemporal.svg?branch=master)](https://travis-ci.org/mlr-org/mlr3spatiotemporal)
[![CRAN Status Badge](https://www.r-pkg.org/badges/version-ago/mlr3spatiotemporal)](https://cran.r-project.org/package=mlr3spatiotemporal)
[![cran checks](https://cranchecks.info/badges/worst/mlr3spatiotemporal)](https://cran.r-project.org/web/checks/check_results_mlr3spatiotemporal.html)
[![CRAN Downloads](https://cranlogs.r-pkg.org/badges/mlr3spatiotemporal)](https://cran.rstudio.com/web/packages/mlr3spatiotemporal/index.html)
[![Lifecycle: maturing](https://img.shields.io/badge/lifecycle-maturing-blue.svg)](https://www.tidyverse.org/lifecycle/#maturing)
[![Coverage status](https://codecov.io/gh/mlr-org/mlr3spatiotemporal/branch/master/graph/badge.svg)](https://codecov.io/github/mlr-org/mlr3spatiotemporal?branch=master)
<!-- badges: end -->

@@

```{r setup, include=FALSE}
set.seed(123)
```

>>>>

Spatio-temporal extensions for mlr3.

<!-- badges: start -->
[![Travis build status](https://travis-ci.org/mlr-org/mlr3spatiotemporal.svg?branch=master)](https://travis-ci.org/mlr-org/mlr3spatiotemporal)
[![cran checks](https://cranchecks.info/badges/worst/mlr3spatiotemporal)](https://cran.r-project.org/web/checks/check_results_mlr3spatiotemporal.html)
[![Lifecycle: maturing](https://img.shields.io/badge/lifecycle-maturing-blue.svg)](https://www.tidyverse.org/lifecycle/#maturing)
[![Coverage status](https://codecov.io/gh/mlr-org/mlr3spatiotemporal/branch/master/graph/badge.svg)](https://codecov.io/github/mlr-org/mlr3spatiotemporal?branch=master)
<!-- badges: end -->

@@

```{r setup, include=FALSE}
set.seed(123)
knitr::opts_chunk$set(fig.path = "man/figures/README-")
```
